\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{PS1}
\author{Kyle Davis}

\begin{document}
\maketitle


\section{}
My interests in economics are more specific to sports. I'm wanting to look at the affect of new stadiums but I have not really decided towards the affect on the community in the economic sense or more of the financial impact on a team. I have a finance background so the latter has more appeal to me but there is much more information on the former so I'm still brainstorming it. Data science is a massively growing field especially in baseball. Ever since 'Moneyball' every major league team has a team of analysts analyzing on both the business and performance side. This class had several reasons for me to take it, one data science is an area I can identify a weakness and with my finance undergrad I feel that this might be a class that can help with a weakness of mine. Another reason is I'm better at the finance aspect as compared to the econ side so this can also boost some skills in that regard. I've been told I have a bit of an old soul and it shows with technology, I am so slow with it so I'd like to be able to do some meaningful things with it not just PowerPoint. The last reason is Colton Steele told me I would like this class and I trust it. If it would allowed I would like to do a project on the effect of new stadiums in major league baseball on revenue or on the surrounding area, but that is also what I'm considering for my research (it's far too broad know but something in that regard). I remember in undergrad I could never 'double-up' on a project and do it twice so to speak but if I could I would absolutely like to do that. My goal is first to gain something valuable to help in my future. My grades are not great at the moment because I got really sick last semester and couldn't finish so I also would like an A but if school doesn't pan out I want to have gained a tool. I plan to get a job for a baseball team and work my up. I want to be the GM for a MLB team and give back to my family and hometown. I have a rather ambitous goal for someone who is not doing great in school but I know no matter what curve ball life throws I can endure. That last line was cheesy but I laughed.


\section{Equation}

\(a^2 + b^2 = c^2\)


\end{document}